---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# quad

<!-- badges: start -->
<!-- badges: end -->

The goal of quad is to provide a framework for fleshing out raster-origin mesh geometry when needed. 

## Installation

You can install the development version of quad from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hypertidy/quad")
```

## Example

This is a basic example which shows you how to expand out the grid when you really need to. 

What is a grid? A *raster* is a six-number specification, *dimension* and *extent*. 

Let's say we have set of raster data, a matrix in R with *ncols*, *nrows* and an extent. 

```{r example}
library(quad)

(dm <- dim(elev)[2:1])

qm <- quad:::qtest(dm)


```

That is the basis for building a partly expanded quadmesh, and it is fast. 

```{r anglr}
##previous we might have used anglr
system.time(anglr::as.mesh3d(elev))

## what if it was much bigger
el <- elev[seq(1, nrow(elev), length.out = 3600), seq(1, ncol(elev), length.out = 1800)]
system.time(anglr::as.mesh3d(el))


## when we use {quad} we have access to the intermediate steps

system.time({
  q <- quad:::qtest(c(3600, 1800))
  vb <- matrix(q, nrow = 4)
  vb[,1] <- scales::rescale(vb[,1], c(-180, 180))
  vb[,2] <- scales::rescale(vb[,2], c(-90, 90))
  
  ## ok still WIP but you see where we're going, anglr needed a 
  ## RasterLayer *object* just to get that extent scaling (!!!)
  ## this is faster and it scales to generic workflows   
})


```
## Code of Conduct
  
Please note that the quad project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
