---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(anglr)
```


# quad

<!-- badges: start -->
<a href="https://gitpod.io/#https://github.com/hypertidy/quad.git">
  <img
    src="https://img.shields.io/badge/Contribute%20with-Gitpod-908a85?logo=gitpod"
    alt="Try with Gitpod"
  />
</a>
[![R-CMD-check](https://github.com/hypertidy/quad/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/hypertidy/quad/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of quad is to provide a framework for fleshing out raster-origin mesh geometry when needed. 

## Installation

You can install the development version of quad from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hypertidy/quad")
```

## Example

This is a basic example which shows you how to expand out the grid when you really need to. 

What is a grid? A *raster* is a six-number specification, *dimension* and *extent*. 

Let's say we have set of raster data, a matrix in R with *ncols*, *nrows* and an extent. 

```{r example}
library(quad)

(dm <- dim(elev)[2:1])

ib <- quad_index(dm)
vb <- quad_vert(dm)
str(ib)
str(vb)
```

That is the basis for building a partly expanded quadmesh, and it is fast. 

```{r anglr}
##previous we might have used anglr
system.time(anglr::as.mesh3d(elev))

## what if it was much bigger
el <- elev[seq(1, nrow(elev), length.out = 3600), seq(1, ncol(elev), length.out = 1800)]
system.time(m3d <- anglr::as.mesh3d(el))
str(m3d)

## when we use {quad} we have access to the intermediate steps

system.time({
  vb <- quad_vert(c(3600, 1800))
  vb <- rbind(matrix(vb, nrow = 2), z = 0.0, h = 1.0)
  vb[,1] <- scales::rescale(vb[,1], c(-180, 180))
  vb[,2] <- scales::rescale(vb[,2], c(-90, 90))

  ib <- matrix(quad_index(c(3600, 1800), ydown = TRUE), nrow = 4L)
  
  ## ok still WIP but you see where we're going, anglr needed a 
  ## RasterLayer *object* just to get that extent scaling (!!!), when
  ## we don't even need an array (it's just dim+extent)
  ## this is faster and it scales to generic workflows   
  
})

str(vb)
str(ib)

```


## TODO


- [x] Mercury
- [ ] ensure alignment of anglr and quad and control with ydown and comparison to rgl is sane and easy
- [ ] provide flat, matrix, dataframe versions of each output (and compare with {geometries})
- [ ] bridge to {textures} and other packages that are for specific outputs (mesh3d, and various 3D formats, and just plotting with vectorized grid.polygon)


## Code of Conduct
  
Please note that the quad project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
